Open Science, Open Plant Pathology

### 2020-04-22 analysis/paper/paper.Rmd
Update info about 5 Year IF

Journals were provided a score for whether they were completely open (TRUE), behind a paywall (FALSE) or a combination (BOTH).
The five-year impact factor for each journal was retreived from (XXXXX) and entered in the notes.

>>>>

Journals were provided a score for whether they were completely open (TRUE), behind a paywall (FALSE) or a combination (BOTH).
The five-year impact factor for 2018 for each journal was retreived from InCites Journal Citation Reports, Clarivate Analytics and entered in a separate sheet in the Google sheets file.
This was downloaded, saved as a .csv file and is left-joined with the article notes using `dplyr::left_join()` for analysis when the `import_notes()` command is executed.
